### 2020-02-20 Article.tex
colorings

\begin{definition} 
	Given a set $\Sigma$ and an hypergraph $G$, a $\Sigma$-coloring 
	of $G$ is a partial function $\chi$ from $V(G)$ to $\Sigma$. 
	A $\Sigma$-hypergraph $(G,\chi)$ is an hypergraph $G$ equipped
	with a $\Sigma$-coloring of $G$, $\chi$. When $\chi$ is understood
	or is not relevant we may omit it and write just $G$ instead of $(G,\chi)$.\par
	Given two $\Sigma$-hypergraphs $(G_1,\chi_1)$ and $(G_2,\chi_2)$,
	a $\Sigma$-isomorphism between them is an hypergraph isomorphism 
	$f:V(G_1)\rightarrow V(G_2)$ satisfying that
	that for any $v\in V(G_1)$ 
	either (1) $\chi_1(v)=\chi_2(f(v))$, or (2) both $\chi_1(v)$ and $\chi_2(f(v))$ 
	are undefined.	A $\Sigma$ automorphism of a $\Sigma$-hypergraph $G$ is a 
	$\Sigma$-isomorphism from $G$ to itself.
	 \par
	Let $(H,\chi_1), (G,\chi_2)$ be two $\Sigma$-hypergraphs. Then a copy of $H$ in $G$ is
	a sub-hypergraph $G_2\subset G$ such that 
	$(H,\chi_1) \simeq_\Sigma (G_2,\chi_2|_{_{G_2}})$.	
\end{definition}

>>>>

\begin{definition} 
	Given a set $\Sigma$ and an hypergraph $G$, a $\Sigma$-coloring 
	of $G$ is a partial function $\chi$ from $V(G)$ to $\Sigma$. 
	A $\Sigma$-hypergraph $(G,\chi)$ is an hypergraph $G$ equipped
	with a $\Sigma$-coloring of $G$, $\chi$. When $\chi$ is understood
	or is not relevant we may omit it and write just $G$ instead of $(G,\chi)$.\par
	Given two $\Sigma$-hypergraphs $(G_1,\chi_1)$ and $(G_2,\chi_2)$,
	a $\Sigma$-isomorphism between them is an hypergraph isomorphism 
	$f:V(G_1)\rightarrow V(G_2)$ satisfying that
	that for any $v\in V(G_1)$ 
	either (1) $\chi_1(v)=\chi_2(f(v))$, or (2) both $\chi_1(v)$ and $\chi_2(f(v))$ 
	are undefined.	A $\Sigma$ automorphism of a $\Sigma$-hypergraph $G$ is a 
	$\Sigma$-isomorphism from $G$ to itself.
	 \par
	Let $(H,\chi_1), (G,\chi_2)$ be two $\Sigma$-hypergraphs. Then a copy of $H$ in $G$ is
	a sub-hypergraph $G_2\subset G$ such that 
	$(H,\chi_1) \simeq_\Sigma (G_2,\chi_2|_{_{G_2}})$.	\par

	Notation: $Copies([n],(G, \chi))$
	Notation: $H\subset_{\Sigma}G$.

\end{definition}
\begin{definition}
	Given a set $\Sigma$, a random $\Sigma$-coloring on $G_n$ is a random 
	partial function $\chi : [n]\rightarrow \Sigma$. \par
	Let $\overline{u}\in [n]^*$, and let $\chi$ be a random coloring on 
	$G_n$. We say that $\chi$ is $\overline{u}$-symmetric if for every 
	$s\in \Sigma$ the probability $\mathrm{Pr}\big(	\chi(v)=s\big)$ is the
	same for all $v\in [n]\setminus\overline{u}$.

\end{definition}

Remark: A random coloring $\chi$ of $G_n$ does not have to be independent from
$G_n$. In fact, in the cases we are going to consider $\chi$ will be determined
by $G_n$.

\begin{definition}
	Let $\Sigma$ be a set, let $\mathcal{F}:=\{H_1, \dots, H_l\}$
	be a finite family of hypergraphs, and
	for each $n\in \N$ let $\chi_n$ be a random coloring of $G_n$. We say that 
	$\chi_n$ is asymptotically $\mathcal{F}$-invariant if for any 
	\begin{itemize}
		\item fixed finite number of copies of hypergraphs from 
		$\mathcal{F}$ in $\N$,
		$G^1,\dots, G^k \in Copies(\N,H_1)\cup \dots \cup Copies(\N,H_l)$.
		\item fixed vertices $\overbrace{v}\in G^1,\dots,G^k$.
		\item fixed labels $\overbar{s}\in \Sigma$
	\end{itemize}  
\end{definition}
